---
title: "R Code for No evidence for adaptive sex ratio adjustment in a cooperatively breeding bird with helpful helpers"
author: "Trey Hendrix"
date: 'Updated: 2023-03-06'
output: 
  github_document:
    toc: true
    toc_depth: 3
---

```{r setup, warning = FALSE, message = FALSE, purl = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  include = TRUE, 
  fig.path = "GRANH1_R_Code_figures_for_markdown/"
)
```

This document contains the R code used to produce the analyses, figures, and supplemental material for the manuscript titled "No evidence for adaptive sex ratio adjustment in a cooperatively breeding bird with helpful helpers." The complete list of authors is Trey C. Hendrix and Christina Riehl. This manuscript is currently under peer review. 

# Required Packages
```{r Packages}
library(readr)
library(dplyr) 
library(lme4)
library(lmerTest)
library(broom.mixed)
library(MuMIn)
library(purrr)
library(stringr)
library(ggplot2)
library(gridExtra)
library(tidyr)
library(DHARMa)
library(car)
library(forcats)
library(knitr)
```

This document was created using: 
```{r Version}
sessionInfo()
```

# Data
The data set analyzed in this study will be made publicly available in the Figshare repository upon publication. The DOI [doi.org/10.6084/m9.figshare.21760979](http://doi.org/10.6084/m9.figshare.21760979) has been reserved, and it will become active if the paper is accepted for publication. We apologize for any inconvenience. The data file necessary to reproduce these analyses is named "GRANH1_anon_221123.csv" and, although it is not currently publicly available, its contents are described in a "README" document in the "Data" folder of this repository. The structure of the data frame is: 
```{r Data Path}
file_path_to_GRANH1_csv <- "/Users/Trey/Documents/All Files/PhD Research/GRANH1/Ani Data Mining R Project/Data/GRANH1_anon_221123.csv" # local file path that will not work on your machine
# This will be updated when the data set is publically released 
```
The structure of these data set is: 
```{r Data frame structure}
df <- read_csv(file_path_to_GRANH1_csv)
glimpse(df, show_col_types = FALSE)
```

# Preparing the data
```{r Standardizing continuous fixed effects}
# Adding a year_location variable to df to denote unique broods
df <- df %>%
  mutate(Year_location = paste(Year, Location, sep = "_"))

# Standardizing continuous fixed effects to reduce multicollinearity
df <- df %>%
  mutate(across(c(Brood_size, Clutch_size, Synchrony), 
                .fns = list(scaled = ~scale(., center = TRUE, scale = TRUE)[,1])))

# Setting factor levels to aid in interpretation
df <- df %>% 
  mutate(Hatch_order = factor(Hatch_order, levels = c("First", "Middle", "Last")), 
         Breeding_pairs = factor(Breeding_pairs, levels = c("Two", "Three")), 
         Hatch_order = relevel(Hatch_order, ref = "First"), 
         Breeding_pairs = relevel(Breeding_pairs, ref = "Two"))

# Fixed effects to be used in models
fixed_effects <- c("Hatch_order", "Brood_size_scaled", 
                   "Clutch_size_scaled","Helper_presence", 
                   "Synchrony_scaled",  "Breeding_pairs", 
                   "Hatch_order:Synchrony_scaled")

# Saving a complete case version of the data frame for use in models
dfcc <- df[complete.cases(select(df, fixed_effects[1:6])),]
```


# Sample sizes reported in manuscript
## Abstract and methods sections
```{r Sex sample sizes}
# All nestlings with sex information 
n_nestlings <- df %>% pull(Band_number) %>% length()
n_broods <- df %>% pull(Year_location) %>% unique() %>% length()
n_locations <- df %>% pull(Location) %>% unique() %>% length() 

paste(n_nestlings, "nestlings of known sex from", n_broods, "broods and", n_locations, "locations.")


# Sample sizes for complete case analysis
n_cc_nestlings <- dfcc %>% pull(Band_number) %>% length()
n_cc_broods <- dfcc %>% pull(Year_location) %>% unique() %>% length()
n_cc_locations <- dfcc %>% pull(Location) %>% unique() %>% length() 

paste("For complete case analysis:", n_cc_nestlings, "nestlings,", n_cc_broods, "broods, and", n_cc_locations, "locations.")
```

## Results section
```{r Sample sizes}
# On average, how many nestlings were sampled in years where a female bias was observed vs. when no bias was observed?
df %>%
  group_by(Year) %>%
  summarize(Mean_sex_ratio = mean(Sex_ratio), 
            n = n(),
            se = sd(Sex_ratio)/sqrt(n)) %>%
  ungroup() %>% 
  mutate(Upper_CI =  Mean_sex_ratio + 1.96*se, 
         Lower_CI =  Mean_sex_ratio - 1.96*se, 
         Bias = case_when(Lower_CI > 0.5 ~ "Male", 
                          Upper_CI < 0.5 ~ "Female", 
                          TRUE ~ "None")) %>% 
  group_by(Bias) %>% 
  summarize(Mean_n = mean(n)) %>% 
  ungroup() %>% 
  mutate(Mean_n = round(Mean_n)) %>% 
  kable()
```

# Population-level sex ratio
To determine if the nestlings in our study population overall deviated from the expected 50:50 sex ratio, we consider two tests that differ in the assumptions they make about the independence of a nestling's sex. These statistical tests (as well as the proportion of our study population that is male) are reported in our results section under the subheading "Population-level sex ratio."
```{r Population-level sex ratio}
# Proportion of our study population that is male
mean(df$Sex) # percentage male  
sum(df$Sex) # total males
length(df$Sex) # total nestlings

# Binomial test: assumes independence of nestlings
binom.test(x = sum(df$Sex), n = length(df$Sex), p = 0.5, alternative = "two.sided", conf.level = 0.95) 

# Wilcoxon signed rank test: A paired test that does not assume that nestlings are independent
wilcoxon_df <- df %>%
  group_by(Year_location) %>%
  summarize(Prop_male = mean(Sex == 1), Prop_female = mean(Sex == 0)) %>%
  ungroup()

wilcox.test(x = wilcoxon_df$Prop_male, y = wilcoxon_df$Prop_female, alternative = "two.sided", paired = TRUE, conf.level = 0.95) 
```


## Figure 1
Sex ratio of nestlings during each year of our study. Error bars show 95% confidence intervals. The dotted line indicates a 50:50 sex ratio, and the number of nestlings sexed in each year is shown above the error bars for each year.
```{r Figure 1}
# ggplot theme that will be reused for plots 
theme_simple <- theme(panel.grid.major = element_blank(), 
                      panel.grid.minor = element_blank(),
                      panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"), 
                      legend.key = element_rect(fill = NA), 
                      text = element_text(size = 15)) 


figure_1 <- df %>%
  group_by(Year) %>%
  summarize(Mean_sex_ratio = mean(Sex_ratio), 
            n = n(),
            se = sd(Sex_ratio)/sqrt(n)) %>%
  ggplot(aes(x = Year, y = Mean_sex_ratio)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = Mean_sex_ratio - 1.96*se, ymax = Mean_sex_ratio + 1.96*se)) + 
  theme_simple + 
  ylab("Proportion of males in nest") + 
  xlab("Year") + 
  geom_hline(yintercept = 0.5, lty = 2, color = "black") + 
  scale_x_continuous(breaks = seq(2007, 2019, 1), labels = paste0("'", str_pad(7:19, width = 2, side = "left", pad = "0"))) + 
  scale_y_continuous(breaks = seq(0, 1, 0.25), limits = c(0, 1)) + 
  geom_text(aes(label = paste(n), y = Mean_sex_ratio + 1.96*se + 0.10), size = 4, color = "black")

figure_1
```

```{r Saving figure 1}
working_directory <- getwd()
project_file_path <- str_remove(working_directory, pattern = fixed("/Scripts")) # This code might need to be modified on your machine to produce the correct file path
output_file_path <- paste0(project_file_path, "/Output")

ggsave(paste0(output_file_path, "/Figure_1.pdf"), figure_1, width = 7, height = 3)
```


# Facultative sex ratio adjustment
Here, we are interested in understanding which variables of interest, if any, can predict the sex of individual nestlings. We use logistic mixed-effects models with a logit link using the glmer function in the lme4 package. All models included nestling sex (coded as “0” for females and “1” for males) as the response variable as well as nest location and year (nested within nest location) as random effects to control for repeated measures. Fixed effects included hatch order, hatching synchrony, brood size, clutch size, the presence of helpers, the number of breeding pairs, and the interaction between synchrony and hatch order. Please see the manuscript text for definitions of these variables. 

In our model selection we use a “best subsets” method. Candidate models are compared to every possible model including a subset of the terms. We consider 80 candidate models (listed below). We do not consider candidate models that included the synchrony by hatch order interaction term unless they also contain synchrony and hatch order separately as fixed effects. Candidate models are evaluated based on Akaike’s Information Criterion adjusted for finite sample sizes (AICc). Models that differed from the top model by less than 2 AICc units are considered to potentially have explanatory value unless they differed from the top model by the addition of a single parameter.

## Generating list of candidate models
This code produces a list of 79 candidate models (80 if you consider a null model with no fixed effects a candidate model):
```{r Making a list of candidate models}
# Function for generating possible combinations of fixed effects 
fixed_effect_combiner <- function(fixed_effects){
  
  fixed_effect_combinations <- lapply(as.list(1:length(fixed_effects)), function(x){combn(fixed_effects, m = x)})
  
  column_getter <- function(l, n){
    lapply(1:ncol(l[[n]]), function(x){l[[n]][,x]})
  }
  
  fixed_effect_list <- lapply(1:length(fixed_effect_combinations), function(x){column_getter(l = fixed_effect_combinations, n = x)}) %>%
    purrr::flatten() %>% 
    lapply(function(x){paste(x, collapse = " + ")}) %>% 
    unlist()
  
  return(fixed_effect_list)
}

# Function for removing models that include interactions made from effects not in the model 
interaction_indexer <- function(fixed_effects_for_one_model){
  
  plus_remover <- function(x){
    str_split(x, pattern = "\\+") %>% 
      unlist() %>% 
      str_trim(side = "both")
  }
  
  all_fixed_effects <- plus_remover(fixed_effects_for_one_model)
  interactions <- all_fixed_effects[str_detect(all_fixed_effects, ":")]
  noninteractions <- all_fixed_effects[!str_detect(all_fixed_effects, ":")]
  
  if(length(interactions) == 0){
    outcome <- TRUE
  } else {
    interactions_split <- lapply(as.list(interactions), function(x){str_split(x, ":")}) %>% 
      unlist() %>%
      unique()
    
    inclusion_test <- mean(interactions_split %in% noninteractions)
    
    outcome <- ifelse(inclusion_test == 1, TRUE, FALSE)
  }
  
  return(outcome)
  
}

# Combining fixed effects
index_of_combinations_to_keep <- lapply(fixed_effect_combiner(fixed_effects), interaction_indexer) %>% unlist() 

candidate_models <- fixed_effect_combiner(fixed_effects)[index_of_combinations_to_keep]
```

## Model Selection
The code below creates a logistic mixed-effects models for each of our 79 candidate models generated above, compares the model to the null model, and then ranks/sorts the models by their AICc scores. 
```{r Modeling functions}
# Modeling functions to be reused

# Function for creating a single model
logistic_model_maker <- function(dv, iv, re, df = dfcc){
  formula <- paste(dv, "~", iv, "+", re, sep = " ") %>% as.formula()
  safe_glmer <- safely(glmer)
  safe_output <- safe_glmer(formula, data = df, family = "binomial", control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
  model <- safe_output$result
}

# Cleaning up terms from the model to make them easier to read
term_cleaner <- function(string){
  new <- str_replace_all(string, fixed("Hatch_orderMiddle"), "Middle nestling")
  new <- str_replace_all(new, fixed("Hatch_orderLast"), "Last nestling")
  new <- str_replace_all(new, fixed("Hatch_orderMiddle:Synchrony_scaled"), "Middle nestling:Synchrony")
  new <- str_replace_all(new, fixed("Hatch_orderLast:Synchrony_scaled"), "Last nestling:Synchrony")
  new <- str_replace_all(new, fixed("Helper_presence"), "Helper")
  new <- str_replace_all(new, fixed("Brood_size_scaled"), "Brood size")
  new <- str_replace_all(new, fixed("Clutch_size_scaled"), "Clutch size")
  new <- str_replace_all(new, fixed("Synchrony_scaled"), "Synchrony")
  new <- str_replace_all(new, fixed("Breeding_pairsTwo"), "Two-pair group")
  new <- str_replace_all(new, fixed("Breeding_pairsThree"), "Three-pair group")
  new <- str_replace_all(new, fixed("_"), " ") # Remove underscores
  return(new)
}


# Function for visualizing a single model
logistic_visualizer <- function(model){
  
  df <- model %>%
    tidy() %>%
    filter(effect == "fixed") %>%
    select(- effect) %>%
    filter(!(term %in% c("(Intercept)", "sd_(Intercept).Location:Year", "sd_(Intercept).Year"))) %>%
    mutate(term = term_cleaner(term)) %>%
    mutate(term = fct_reorder(term, estimate)) %>%
    mutate(lower = estimate - 1.96*std.error,
           upper = estimate + 1.96*std.error)
  
  df %>%
    ggplot(aes(x = estimate, y = term)) + 
    geom_point() + 
    geom_linerange(aes(xmin = lower, xmax = upper)) + 
    labs(x = "Model Estimate", y = "Fixed Effect") + 
    geom_vline(xintercept = 0, lty = 2, color = "red") +
    theme_simple
}

# Function for running a list of models, ranking them, and producing a summary table 
logistic_model_comparer <- function(dv, iv, re, df = df) {
  
  # Complete case analysis
  fixed_effects_vector <- iv %>% str_split(pattern = fixed(" + ")) %>% unlist()
  fixed_effects_vector <- fixed_effects_vector[str_detect(fixed_effects_vector, pattern = fixed(":"), negate = TRUE)]
  df_index <- df[,fixed_effects_vector]
  df <- df[complete.cases(df_index),]
  
  # Running model
  formula <- paste(dv, "~", iv, "+", re, sep = " ") %>% as.formula()
  safe_glmer <- safely(glmer)
  safe_output <- safe_glmer(formula, data = df, family = "binomial", control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
  model <- safe_output$result
  
  # Null model 
  null_formula <- paste(dv, "~", "1",  "+", re, sep = " ") %>% as.formula()
  null_model <- safe_glmer(null_formula, data = df, family = "binomial", control = glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))$result
  
  # Making dataframe 
  model_output <- ifelse(length(safe_output$result) > 0, AICc(safe_output$result), NA_real_)
  error_output <- ifelse(length(safe_output$error) > 0, as.character(safe_output$error), "No error")
  result_df <- tibble(Formula = iv,
                      AICc = model_output,
                      Error = error_output)
  
  # ANOVA
  if(error_output == "No error") {
    anova_df <- anova(model, null_model) %>% tidy() %>% filter(term == "model") %>% select(-c("term", "df"))
    
    final_df <- result_df %>% 
      bind_cols(anova_df)
    
    
  } else {
    final_df <- result_df
  }
  
  return(final_df)
}


add_evidence_ratio_logistic <- function(dv, odf, re, df = dfcc){
  
  null_formula <- paste(dv, "~", "1",  "+", re, sep = " ") %>% as.formula()
  null_model <- glmer(null_formula, data = df, family = "binomial", control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
  
  df <- data.frame(Formula = "Null", 
                   AICc = AICc(null_model),
                   logLik = logLik(null_model)) %>% 
    bind_rows(odf) %>%
    arrange(AICc) %>% 
    mutate(delta_AICc = abs(AICc - min(AICc)),
           rel_likelihood = exp(-1/2 * delta_AICc),
           w = rel_likelihood/(sum(rel_likelihood))) %>%
    arrange(desc(w)) %>% 
    mutate(w_rank = 1:nrow(.))
  
  null_w <- df %>%
    filter(Formula == "Null") %>%
    pull(w)
  
  null_logLik <- df %>%
    filter(Formula == "Null") %>%
    pull(logLik)
  
  final_df <- df %>%
    mutate(pseudo_R2 = 1 - logLik/null_logLik)
  
  
  final_df$evidence_ratio <- NA
  
  for(i in 1:(nrow(final_df)-1)){
    final_df$evidence_ratio[i] <- final_df$w[i]/final_df$w[i+1]
  }
  
  final_df <- final_df %>%
    arrange(AICc) %>%
    mutate(evidence_ratio = round(evidence_ratio, digits = 3)) %>%
    select(-w_rank)
  
  return(final_df)
}
```


```{r Running Models}
# Global model 
global_model <- logistic_model_maker(dv = "Sex", iv = candidate_models[length(candidate_models)], re = "(1|Year/Location)", df = dfcc)
logistic_visualizer(global_model) 
summary(global_model) 

# Model selection (summary table)
models_df <- lapply(as.list(candidate_models), 
                    function(x){logistic_model_comparer(dv = "Sex", iv = x, re = "(1|Year/Location)", df = dfcc)}) %>%
  bind_rows() %>%
  arrange(AICc) %>%
  mutate(delta_AICc = abs(AICc - min(AICc))) %>%
  select(Formula, delta_AICc, AICc, everything())

models_df <- add_evidence_ratio_logistic(dv = "Sex", odf = models_df, re = "(1|Year/Location)", df = df)
```

## Table 1
Best subset models predicting the sex of individual nestlings. All models are logistic mixed-effect models with nest location and year included as a random intercept. Each model is compared to a null model run on the same dataset including only random effects using a likelihood ratio test. Models with ∆AICc < 2 are shown as well as global and null models. All continuous variables (i.e., clutch size, brood size, synchrony) were scaled and centered to reduce multicollinearity. 
```{r Table 1}
table_1 <- models_df %>%
  mutate(Formula = ifelse(Formula == candidate_models[length(candidate_models)], "Global", Formula)) %>% 
  filter(delta_AICc < 2 | Formula %in% c("Global", "Null")) %>% 
  mutate(Formula = term_cleaner(Formula))

# Removing uninformative parameters (Arnold 2010)
table_1 <- table_1 %>% 
  filter(!(Formula %in% c("Hatch order + Clutch size + Helper", "Hatch order + Clutch size + Synchrony", "Hatch order + Clutch size + Breeding pairs"))) 

# Tidying up table 1
table_1 <- table_1 %>%
  select(Fixed_effects = Formula, delta_AICc, AICc, chi_sq = statistic, P_value = p.value, w, pseudo_R2) %>% 
  mutate(across(where(is.numeric), ~ round(.x, 3)))

table_1 %>% 
  kable()
```

```{r Saving table 1}
write_csv(table_1, paste0(output_file_path, "/Table_1.csv"))
```

```{r Top model}
# Top performing model (not significant)
top_model <- logistic_model_maker(dv = "Sex", iv = "Hatch_order + Clutch_size_scaled", re = "(1|Year/Location)", df = dfcc) 
logistic_visualizer(top_model)
summary(top_model) 
```

## Table S1
Variance inflation factors for the fixed effects included in the global model predicting the sex of individual nestlings. These estimates were generated using the “vif” function from the “car” package (Fox and Weisberg 2019).
```{r vif for global model}
table_s1 <- vif(global_model)  %>%
  as_tibble() %>% 
  mutate(Predictor = row.names(vif(global_model)), 
         Predictor = term_cleaner(Predictor), 
         VIF = round(GVIF, 3)) %>% 
  select(Predictor, VIF)

table_s1 %>% 
  kable()
```

```{r Saving table s1}
write_csv(table_s1, paste0(output_file_path, "/Table_S1.csv"))
```


## Figure 2
Sex ratio of nestlings with respect to (a) whether or not a helper was observed at their nest and (b) position in hatch order. In both, error bars show 95% confidence intervals, the dotted line indicates a 50:50 sex ratio, and the number of nestlings sexed in each year is shown above each error bar.
```{r Figure 2}
helper_plot <- df %>%
  filter(!is.na(Helper_presence)) %>% 
  group_by(Helper_presence) %>%
  summarize(Mean_sex = mean(Sex), 
            n = n(), 
            se = sd(Sex)/sqrt(n)) %>%
  ggplot(aes(x = Helper_presence, y = Mean_sex)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = Mean_sex - 1.96*se, ymax = Mean_sex + 1.96*se), width = 0.75) + 
  geom_text(aes(label = paste(n), y = Mean_sex + 1.96*se + 0.10), color = "black") + 
  theme_simple + 
  ylab("Proportion of males in nest") + 
  xlab("Helper Presence") + 
  scale_x_continuous(breaks = seq(0, 1, 1), labels = c("No helpers", "Helpers")) +
  scale_y_continuous(breaks = seq(0, 1, 0.25), limits = c(0, 1)) + 
  geom_hline(aes(yintercept = 0.5), color = "black", lty = 2) + 
  ggtitle("a.") 

hatch_fraction_plot <- df %>%
  filter(!is.na(Hatch_order)) %>% 
  group_by(Hatch_order) %>%
  summarize(Mean_sex = mean(Sex), 
            n = n(), 
            se = sd(Sex)/sqrt(n)) %>%
  ungroup() %>%
  mutate(Hatch_order = factor(Hatch_order, levels = c("First", "Middle", "Last"))) %>%
  ggplot(aes(x = Hatch_order, y = Mean_sex)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = Mean_sex - 1.96*se, ymax = Mean_sex + 1.96*se), width = 0.75) + 
  geom_text(aes(label = paste(n), y = Mean_sex + 1.96*se + 0.10), color = "black") + 
  theme_simple + 
  ylab("") + 
  xlab("Position in hatch order") + 
  scale_y_continuous(breaks = seq(0, 1, 0.25), limits = c(0, 1)) + 
  geom_hline(aes(yintercept = 0.5), color = "black", lty = 2) + 
  ggtitle("b.")

figure_2 <- grid.arrange(helper_plot, hatch_fraction_plot, nrow = 1, respect = TRUE)
```

```{r Saving figure 2}
ggsave(paste0(output_file_path, "/Figure_2.pdf"), figure_2, width = 7, height = 3)
```


## Table S2
Please not that the formatting of this table has not been reproduced below. Instead, I present the information as 4 seperate tables. The caption for this table presented in the Supplementary Information is: 
"Parameters and random effect estimates for (a) the best-fit and (b) global logistic mixed effects models predicting the sex of individual ani nestlings. Significant parameters (p<0.05) have been bolded. The reference levels for the categorical fixed effects are: first hatching (for hatch order) and two-pair group (for breeding pairs)."
```{r Table s2 best fit}
# AICc for top model presented in table 
AICc(top_model) %>% round(1)

# Best-fit model table S2
top_short_table <- top_model %>% 
  tidy() %>%
  mutate(term = case_when(group == "Location:Year" ~ "sd_(Intercept)|Location:Year", 
                          group == "Year" ~ "sd_(Intercept)|Year",
                          is.na(group) ~ term)) %>%
  select(- c("group", "effect"))

set.seed(42) # for reproducibility 
top_cis <- lme4::confint.merMod(top_model, oldNames = FALSE, method = "profile") 

top_cis_df <- top_cis %>%
  as.data.frame() %>%
  mutate(term = rownames(.)) %>%
  mutate(CI_lower = `2.5 %`, 
         CI_upper = `97.5 %`) %>%
  select(term, CI_lower, CI_upper)

rownames(top_cis_df) <- NULL

table_s2_best_fit <- top_short_table %>%
  left_join(top_cis_df, by = "term") %>%
  mutate_if(is.numeric, function(x){round(x, 3)}) %>% 
  mutate(term = term_cleaner(term))

table_s2_best_fit %>% 
  kable()
```

```{r Saving table s2 best fit}
write_csv(table_s2_best_fit, paste0(output_file_path, "/Table_S2_best_fit.csv"))
```

```{r Table s2 global}
# AICc for global model presented in table  
AICc(global_model) %>% round(1)

global_short_table <- global_model %>% 
  tidy() %>%
  mutate(term = case_when(group == "Location:Year" ~ "sd_(Intercept)|Location:Year", 
                          group == "Year" ~ "sd_(Intercept)|Year",
                          is.na(group) ~ term)) %>%
  select(- c("group", "effect"))


set.seed(42) # for reproducibility 
global_cis <- lme4::confint.merMod(global_model, oldNames = FALSE, method = "profile") 

global_cis_df <- global_cis %>%
  as.data.frame() %>%
  mutate(term = rownames(.)) %>%
  mutate(CI_lower = `2.5 %`, 
         CI_upper = `97.5 %`) %>%
  select(term, CI_lower, CI_upper)

rownames(global_cis_df) <- NULL


table_s2_global <- global_short_table %>%
  left_join(global_cis_df, by = "term") %>%
  mutate_if(is.numeric, function(x){round(x, 3)}) %>% 
  mutate(term = term_cleaner(term))

table_s2_global %>% 
  kable()
```

```{r Saving table s2 global}
write_csv(table_s2_global, paste0(output_file_path, "/Table_S2_global.csv"))
```


# Assessing model residuals using DHARMa
Here, we use the “DHARMa” package to visualize the global model's residuals.
```{r DHARMa set up}
model_interrogator <- function(model, fixed_effects, df){
  
  # Running simulation
  sim <- simulateResiduals(fittedModel = model, plot = T, n = 1000)
  
  # General histogram looking for uniform distribution
  hist(sim)
  
  lapply(as.list(str_split(fixed_effects, pattern = fixed(" + "), 
                           simplify = TRUE)), 
         function(x){
           predictor <- unlist(df[, x])
           
           if(str_detect(x, fixed("scaled"))){
             predictor <- round(predictor, 3)
           }
           
           boxplot(sim$scaledResiduals ~ predictor, 
                   xlab = x, 
                   ylab = "Scaled Residuals")
         })
  
  
  # Goodness-of-fit tests
  testResiduals(sim)
  testZeroInflation(sim)
  testTemporalAutocorrelation(sim, df$unique_relative_time)
}
```


```{r Global model DHARMa}
model_interrogator(global_model, "Hatch_order + Brood_size_scaled + Clutch_size_scaled + Helper_presence + Synchrony_scaled + Breeding_pairs", dfcc)
```

## Figure S1
Scaled residual plots of the global model predicting nestling sex.
```{r Figure s1}
simulateResiduals(fittedModel = global_model, n = 1000, plot = T)
```

```{r Saving figure s1}
# Saving this figure separately as Figure s1
figure_s1 <- simulateResiduals(fittedModel = global_model, n = 1000)
pdf(paste0(output_file_path, "/Figure_S1.pdf"))
plot(figure_s1)
dev.off()
```
